### 2023-06-27 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

  %-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.50}
\begin{tabularx}{\textwidth}{Xccccc}
\toprule
Detector &  Rapidity &  Target & Lepton sign & Acceptance  & Performance \\
\midrule
\multirow{2}{*}{FASER$\nu$}  &   &   Tungsten  & \multirow{2}{*}{muons}      &     &         \\
  &   &   (1.1 ton)  &       &     &         \\
\midrule
\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &       &       &       \\
  &   &  (0.83 ton)   &       &       &       \\
\midrule
\midrule
\multirow{3}{*}{FASER$\nu$2}  &   & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{only muons}     &   $E_\ell \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
  &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.5$   &   $\delta \theta_\ell \sim 1$ mrad      \\
  &   &     &       &  reconstructed $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\
\midrule
\multirow{3}{*}{AdvSND~(far)}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{only muons}    &  $E_\mu \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
  &   &   \multirow{2}{*}{(5 ton)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
  &   &     &       &  reconstructed $E_h$   &           \\
\midrule
\multirow{3}{*}{FLArE}  & \multirow{3}{*}{Liquid Argon}  &  & \multirow{3}{*}{ maybe muons}  &  $E_\mu \lsim 2$ GeV, $E_e \lsim 1$ TeV    &    $\delta E_e \sim 5\% $ \\
&   &     &   & $\theta_\mu \lsim 0.4$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $ mrad   \\
 &   &     &  & reconstructed $E_h$  &    $\delta E_h \sim 30\% $   \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small For each of the far-forward LHC neutrino experiments considered
  in this work, we indicate their rapidity coverage, target material, whether
  they can identify the sign of the outgoing charged lepton,
  the detector acceptance for the charged lepton and hadronic final state,
  and the expected reconstruction performance.
  %
  We consider separately the acceptance and performance for electron and muon
  neutrinos.
  %
  Tau neutrinos have much lower production rates and are not considered in this study.
  %
  See the description of each experiment in the text for more details.
  \label{tab:FPF_experiments}
}
\end{table}
%-----------------------------------------------------------------

>>>>

  %-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.50}
\begin{tabularx}{\textwidth}{Xccccc}
\toprule
Detector &  Rapidity &  Target & Lepton sign & Acceptance  & Performance \\
\midrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small For each of the far-forward LHC neutrino experiments considered
  in this work, we indicate their rapidity coverage, target material, whether
  they can identify the sign of the outgoing charged lepton,
  the detector acceptance for the charged lepton and hadronic final state,
  and the expected reconstruction performance.
  %
  We consider separately the acceptance and performance for electron and muon
  neutrinos.
  %
  Tau neutrinos have much lower production rates and are not considered in this study.
  %
  See the description of each experiment in the text for more details.
  \label{tab:FPF_experiments}
}
\end{table}
%-----------------------------------------------------------------
